Analyzing Arrest Patterns and Racial Representation in Toronto

### 2024-12-03 paper/paper.qmd
Adding estimand in introduction

>>>>

The study aims to estimate the disparity in arrest rates between racial groups in Toronto, conditioned on demographic and socioeconomic variables such as age, income level, and neighborhood characteristics. Specifically, it seeks to quantify the proportion of arrests attributable to racial representation disparities, holding other factors constant.
